Group meetings

### 2023-06-06 diapo/05-06-23_meeting/main.tex
New file, plus pre change to slides
New figure + updated diapo
New version of the slides
One more help i need

  \begin{frame}<1>[label=prob]
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item<1-> The memory doesn't output the right values
      \item<2-> The memory input seems to be active for too long
    \item<3-> The output result isn't what is expected    \end{itemize}
  \end{frame}

@@

  \againframe<3>{prob}
  \begin{frame}{Problems/doubts}
    The output is ~0.791 V. This is $-1.09$ and should be $0.015$

    \centering
    \includegraphics[width=1\textwidth]{fulltrial1/fulltrial1-final-res}
  \end{frame}

@@

  \begin{frame}{Networking and sharing}
    \begin{tikzpicture}
      \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help}

>>>>

\begin{frame}<1>[label=prob]
  \frametitle{Problems/doubts}
  \begin{itemize}
    \item<1-> The memory doesn't output the right values
    \item<2-> The memory input seems to be active for too long
    \item<3-> The output of the sigmoid doesn't look right
    \item<4-> The output result isn't what is expected
  \end{itemize}
\end{frame}

@@

\againframe<3>{prob}
\begin{frame}{Problems/doubts}
  Here we can see that the output of the sigmoid isn't right
  \begin{figure}[!tbp]
    \centering
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{fulltrial1/sigmoid-prob.png}
    \end{minipage}
    \hspace{20pt}
    \begin{minipage}[b]{0.4\textwidth}
      \centering
      \includegraphics[width=\textwidth]{activation/sigmoid-prob}
    \end{minipage}
  \end{figure}
\end{frame}

\againframe<4>{prob}
\begin{frame}{Problems/doubts}
  The output is ~0.791 V. This is $-1.09$ and should be $0.015$

  \centering
  \includegraphics[width=\textwidth]{fulltrial1/fulltrial1-final-res}
\end{frame}

@@

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help\\- I would need the feature size of a typical memristor}
